### 2022-11-14 proof.tex
Adding Facts

If Procedure 2 terminates, then
$k$-resilience does not hold.
It remains to show that Procedure 2 terminates whenever $k$-resilience does not hold.

>>>>

If Procedure 2 terminates, then
$k$-resilience does not hold.
It remains to show that Procedure 2 terminates whenever $k$-resilience does not hold.
Assume $ post^*(s) \cap J \not\subseteq I^k$, then there exists $a \in post^*(s) \cap J$ such that $a \not\in I^k$. Since $post^*(s) = \bigcup_{n} post^{\leq n}(s)$, then 
$a \in post^*(s)$
implies
there exists
$n_a$
such that
$a \in post^{\leq n_a}(s)$.
Hence,  $post^{\leq n_a}(s) \cap J$ contains an element not in 
$I^k$,
and Procedure 2 terminates.
\end{enumerate}
